### 2018-05-01 paper/security-discussion.tex
Adds discussion on needed privacy of RPS scheme

>>>>

Finally, we would also need the random peer sampling to be privacy preserving.
Consider the following scenario.
Alice requests a set of peers, say \(\{d_1, \dotsc, d_n\}\).
If \(d_i\) interacts in each sampling operation resulting in \(d_i\) being in 
the sample, then \(d_i\) can generate a new public key \(\pk_d^{(j)}\) for each 
sample \(j\).
This means that, if Alice sampled \(d_i\), she knows the public key 
\(\pk_i^{(j)}\), and if \(d_i\) knows it is included in Alice's sample, then it 
will also know a route belongs to Alice whenever \(\pk_i^{(j)}\) is used to 
encrypt the header.
\Ie every node on Alice's route would know that Alice is either the source or 
the destination.
When running the protocol, Alice only creates one part of the route and Bob 
creates the other.
This means that no device knows both ends of the route unless they collude.
